Blueprint for efficient nuclear spin characterization in color center

### 2024-02-02 article.tex
the paper is ready? @majidzahedian please proof read, then i will also proof read and submit

\label{sec:discussion}
\begin{figure*}%[htbp]
	\begin{center}
		\includegraphics[width=1.0\textwidth]{pict/cov_compare_vad.pdf}
		\caption{Visualisation of the CramerRao bound for various protocols on existing nuclear spin dataset from \cite{Abobei2019}}
		\label{fig:cov}
	\end{center}
\end{figure*}
Fig. \ref{fig:ddeseem} shows the Fourier transform of the signal.
Zooming into the area close to the Larmor frequency reveals the weakly coupled nuclei.
Each nuclear spin has two peaks in the spectrum referring to $\omega_a$ and $\omega_b$. Expanding the resonance frequencies up to first order with respect to hyperfine coupling shows that nuclear spins appear in order of their coupling strength, making their characterization rather straightforward.
To observe the weakly coupled nuclei more pronouncedly, one can use the DD-ESEEM sequence by adding more $\pi$ pulses in the entangling periods.
To distinguish other nuclei, extra measurements are required.
One method is to use two-dimensional hyperfine correlation spectroscopy (2D Hyscore) \cite{vorobyov2022addressing}.
However, this method is rather time-consuming as two time variables have to be swept.
Optimum time sampling techniques might be used to optimize the timing of 2D sampling.
Here we suggest an alternative way, which is conventionally used in ESR, i.e., sweeping the $\tau$ parameter and keeping track of the frequency amplitude as a function of $\tau$.
Two frequencies that belong to the same nucleus are correlated because the modulation depth oscillates with blind spot terms of both frequencies $\sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2})$.
Fig. \ref{fig:4} shows two frequencies going to bright and blind spots simultaneously.
Hence, by taking a two-dimensional correlation of the spectrum, one can deduce which two frequencies are correlated and belong to the same nucleus.

@@

%\subsection{Advanced filters}
In this work we performed a theoretical and numerical comparison of various ESEEM methods for the purpose of characterisation of the nuclear spin clusters around S=1 and S=1/2 type of defects.
We found, that while for S=1 systems, modified spin echo sequences, e.g. CPMG and XY-N, are most suited for single nuclear spin qubit spectroscopy, for S=1/2 system they are limited in performance. 
We see, that a correlation type sequences, e.g. 3,5 pulse ESEEM present a more potential for characterisation of a diluted nuclear spin bath, and perform at least similar to the S=1 case. 
We believe, that this method boast large potential for preliminary screening of nuclear spin clusters for S=1/2 potential qubit candidate systems, such as G-IV defects in diamond. Additionally, our method does not require strong microwave pulse fields, since the pulses do not require to cope with nuclear spin Larmour frequency.

>>>>

\label{sec:discussion}
\begin{figure*}%[htbp]
	\begin{center}
		\includegraphics[width=1.0\textwidth]{pict/cov_compare_vad.pdf}
		\caption{Visualisation of the CramerRao bound for various protocols on existing nuclear spin dataset from \cite{abobeih2019atomic}}
		\label{fig:cov}
	\end{center}
\end{figure*}
Fig. \ref{fig:ddeseem} shows the Fourier transform of the signal.
Zooming into the area close to the Larmor frequency reveals the weakly coupled nuclei.
Each nuclear spin has two peaks in the spectrum referring to $\omega_a$ and $\omega_b$. Expanding the resonance frequencies up to first order with respect to hyperfine coupling shows that nuclear spins appear in order of their coupling strength, making their characterization rather straightforward.
To observe the weakly coupled nuclei more pronouncedly, one can use the DD-ESEEM sequence by adding more $\pi$ pulses in the entangling periods.
To distinguish other nuclei, extra measurements are required.
One method is to use two-dimensional hyperfine correlation spectroscopy (2D Hyscore) \cite{vorobyov2022addressing}.
However, this method is rather time-consuming as two time variables have to be swept.
Optimum time sampling techniques might be used to optimize the timing of 2D sampling.
Here we suggest an alternative way, which is conventionally used in ESR, i.e., sweeping the $\tau$ parameter and keeping track of the frequency amplitude as a function of $\tau$.
Two frequencies that belong to the same nucleus are correlated because the modulation depth oscillates with blind spot terms of both frequencies $\sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2})$.
Fig. \ref{fig:4} shows two frequencies going to bright and blind spots simultaneously.
Hence, by taking a two-dimensional correlation of the spectrum, one can deduce which two frequencies are correlated and belong to the same nucleus.

@@

%\subsection{Advanced filters}
In this work we performed a theoretical and numerical comparison of various ESEEM methods for the purpose of characterisation of the nuclear spin clusters around S=1 and S=1/2 type of defects.
We found, that while for S=1 systems, modified spin echo sequences, e.g. CPMG and XY-N, are most suited for single nuclear spin qubit spectroscopy, for S=1/2 system they are limited in performance. 
We see, that a correlation type sequences, e.g. 3,5 pulse ESEEM present a more potential for characterisation of a diluted nuclear spin bath, and perform at least similar to the S=1 case. 
We believe, that this method boast large potential for preliminary screening of nuclear spin clusters for S=1/2 potential qubit candidate systems, such as G-IV defects in diamond. Additionally, our method does not require strong microwave pulse fields, since the pulses do not require to cope with nuclear spin Larmour frequency. 
In this work we show various sensing methods, while we dont touch the estimator performance. 
We believe, that this has to be considered in conjuction with adaptive and optimal strategies for controlling the experimental parameters, e.g. Bayessian Optimal Experimental Design or Machine Learning for increasing the efficiency of estimation.
